---
title: "Untitled"
author: "Stacey Jackson"
date: "28/03/2019"
output: word_document
---


```{r}
library("caret")
library("dplyr")
ExistingProductAttributes<-read.csv(file="/Users/staceyjackson/Dropbox (Personal)/Ubiqum/DataAnalytics2/ProductTypePrediction/Data/existingproductattributes2017.csv", header=TRUE, sep=",")
NewProductAttributes<-read.csv(file="/Users/staceyjackson/Dropbox (Personal)/Ubiqum/DataAnalytics2/ProductTypePrediction/Data/newproductattributes2017.csv", header=TRUE, sep=",")

```
Dummify
```{r}
newDataFrame<-dummyVars("~.",data=ExistingProductAttributes)
readyData <- data.frame(predict(newDataFrame,newdata = ExistingProductAttributes))
attributes(readyData)
names(readyData)
```
Check variables
```{r}
str(readyData)
```
Summary
```{r}
summary(readyData)
```
Delete attributes with missing values
```{r}
readyData$BestSellersRank <- NULL
summary(readyData)
```
correlation
```{r}
corrData <- cor(readyData)
corrData
```
Heat map
```{r}
library(corrplot)
corrplot(corrData)
corrplot(corrData,type="upper",tl.pos="td",method="circle",tl.cex = 0.5,tl.col='black',diag=FALSE)
```


columns to remove to reduce pair-wise correlations - corresponds to 3-star Reviews, 5-star Reviews and 2-star Reviews
```{r}

findCorrelation(corrData, cutoff = .90, verbose = FALSE)

findCorrelation(corrData, cutoff = .90, verbose = TRUE)

names(readyData)

```
####1.Remove Product Number, x5-star review, x3-star review, x1-star review, BestSellerRank and product types####
```{r}
readyData2 <- readyData[-c(1:13,15,17,19)]
```
####1.1Plots####
```{r}
p <- ggplot(data=readyData2, mapping=aes(x=Volume))
p + geom_histogram(bins=8)
boxplot(readyData2$Volume)


p <- ggplot(data=readyData2, mapping=aes(x=PositiveServiceReview))
p + geom_histogram(bins=8)
boxplot(readyData2$PositiveServiceReview)

p <- ggplot(data=readyData2, mapping=aes(x=NegativeServiceReview))
p + geom_histogram(bins=8)
boxplot(readyData2$NegativeServiceReview)

p <- ggplot(data=readyData2, mapping=aes(x=x4StarReviews))
p + geom_histogram(bins=8)
boxplot(readyData2$x4StarReviews)

p <- ggplot(data=readyData2, mapping=aes(x=x2StarReviews))
p + geom_histogram(bins=8)
boxplot(readyData2$x2StarReviews)

p <- ggplot(data=readyData2, mapping=aes(x=Price))
p + geom_histogram(bins=8)
boxplot(readyData2$Price)
```
Remove Volume<=3,000
```{r}
library(dplyr)
readyData2<-readyData2%>%
  filter(Volume<=3000)
```
Plots of volume and other variables
```{r}

p <- ggplot(data = readyData2, mapping = aes(x = Volume, y = ProfitMargin, color=ProfitMargin))
p + geom_point()

p <- ggplot(data = readyData2, mapping = aes(x = Price, y = Volume))
p + geom_point()

p <- ggplot(data = readyData2,mapping = aes(x = Volume, y = PositiveServiceReview))
p + geom_point(size=3) +
    coord_flip()

p <- ggplot(data = readyData2, mapping = aes(x = Volume, y = x4StarReviews))
p + geom_point(size=3) +
    coord_flip()
```

Training and test sets
```{r}
trainSize <- round(nrow(readyData2)*0.7)
testSize <- nrow(readyData3)-trainSize
trainSize

set.seed(998)
training_indices <- sample(seq_len(nrow(readyData2)),size = trainSize)
trainSet<-readyData2[training_indices,]
testSet <- readyData2[-training_indices,]


```


Linear model
```{r}

lmModel <- lm(formula = Volume~.,data=trainSet)
summary(lmModel)

```
```{r}
predictlmModel<-predict(lmModel,testSet)
predictlmModel
```

plot
```{r}
plot(lmModel)
```

Loop to investigate three base models
```{r}
a <- c("knn","rf","svm")
comp_model <- c()

for (i in a){
  model <- train(Volume~.,trainSet,method=i,trControl="cv")
  pred <- predict(model,testSet)
  metric<-postResample(testSet$Volume,pred)
  comp_model<-cbind(metric,comp_model)
}
colnames(comp_model) <- a
comp_model
```
SVM
```{r}
svm_Linear <- train(Volume ~., data = trainSet, method = "svmLinear", trControl=fitControl, preProcess = c("center", "scale"), tuneLength = 10)
svm_Linear
varImp(svm_Linear)
svm_Linear$bestTune
prediction<-predict(svm_Linear,testSet)
postResample(pred = prediction,obs=testSet$Volume)
prediction
```

KKN model
```{r}
fitControl<-trainControl(method="repeatedcv",number = 5,repeats=1)
KNNfit1<-train(Volume~.,data=trainSet,method="knn",trControl=fitControl,preProcess = c("center","scale"), tuneLength=20)
KNNfit1
varImp(KNNfit1)
KNNfit1$bestTune
prediction1<-predict(KNNfit1,testSet)
postResample(pred = prediction1,obs=testSet$Volume)


```
Random Forest
```{r}
rfGrid<-expand.grid(mtry=c(1,2,3,4,5))
rfFit1<-train(Volume~.,data=trainSet,method="rf",trControl=fitControl,tuneGrid=rfGrid,importance=TRUE)
rfFit1
rfFit1$bestTune
varImp(rfFit1)
prediction2<-predict(rfFit1,testSet)
postResample(pred = prediction2,obs=testSet$Volume)
prediction2

```
FINAL MODEL - rf with positive servic review, 4-star review and recommend product
```{r}
rfGrid<-expand.grid(mtry=c(1,2,3,4,5))
rfFit_Final<-train(Volume~PositiveServiceReview + x4StarReviews + Recommendproduct,data=trainSet,method="rf",trControl=fitControl,tuneGrid=rfGrid,importance=TRUE)
rfFit_Final
rfFit_Final$bestTune
varImp(rfFit_Final)
prediction<-predict(rfFit_Final,testSet)
postResample(pred = prediction,obs=testSet$Volume)
prediction

errorMetrics <- function(predictedValues, actualValues) {
  absoluteError <- predictedValues - actualValues
  square_error <- absoluteError * absoluteError
  data.frame(absoluteError, square_error)
}

errors<-errorMetrics(prediction,testSet$Volume)

plot(testSet$Volume, errors$absoluteError)
plot(testSet$Volume,errors$square_error)

p<-ggplot(data=testSet, aes(x=Volume, y=errors$absoluteError, color=Volume))
p+geom_point() +
  labs(x="Volume", y= "Absolute Errors", title = "Test set: absolute errors")

p<-ggplot(data=testSet, aes(x=Volume, y=errors$square_error, color=Volume))
p+geom_point() +
  labs(x="Volume", y= "Square Errors", title = "Test set: square errors")

p<-ggplot(data=testSet, aes(x=Volume, y=errors$absoluteError, color=Volume))
p+geom_smooth(method = "loess") +
  scale_x_log10() +
  labs(x="Volume", y= "Absolute Errors", title = "Test set: absolute errors")

p<-ggplot(data=testSet, aes(x=Volume, y=errors$square_error, color=Volume))
p+geom_smooth(method = "loess") +
  scale_x_log10() +
  labs(x="Volume", y= "Square Errors", title = "Test set: square errors")


```

Final predictions
```{r}
newDataFrame<-dummyVars("~.",data=NewProductAttributes)
NewProductAttributes2 <- data.frame(predict(newDataFrame,newdata = NewProductAttributes))


NewProductAttributes2<-NewProductAttributes2[-c(1:14,15,17,19)] 
names(NewProductAttributes2)
finalPred<-predict(rfFit_Final,NewProductAttributes2)
finalPred
```

